First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-28 eg6-letters/coherent/dvcs_he4_prl.tex
removed figure 2 and cleaned the related text.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. Presented in FIG.~\ref{fig:RTPC} are a 
picture of RTPC installed in the experimental hall and a diagram showing the 
basic detection technique. The $^4$He gaseous target, a $25$ cm long Kapton 
straw with $27~\mu$m thick wall, was part of the RTPC assembly and installed on 
the axis of the detector. The RTPC was calibrated specifically for the 
detection of $^4$He nuclei using elastic scattering with a 1.2~GeV electron 
beam.

\begin{figure}[tb]
\vspace{-1.1cm}
\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
\vspace{-1.1cm}
\caption{Left: A picture of the E08-024 RTPC before insertion into the 
   solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the 
   beam direction. An illustration of a $^4$He track originating from the 
   pressurized straw target is shown along with the electrons produced in the 
   drift region.}
\label{fig:RTPC}
\end{figure}

>>>>

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. The RTPC is a $20$ cm long cylinder 
with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
target. The target is a $25$ cm long and $6$ mm diameter Kapton straw with 
$27~\mu$m thick wall. The RTPC was calibrated specifically for the detection of 
$^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

%\begin{figure}[tb]
%\vspace{-1.1cm}
%\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
%\vspace{-1.1cm}
%\caption{Left: A picture of the E08-024 RTPC before insertion into the 
%solenoid. Right: A cross section of the E08-024 RTPC perpendicular to the beam 
%direction. An illustration of a $^4$He track originating from the pressurized 
%straw target is shown along with the electrons produced in the drift region.}
%\label{fig:RTPC}
%\end{figure}
